IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/extensions.tex
Pass on limitations

%while
%LIO implements a labeled file system, used in server-side web
%applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section we show how to extend our framework with several such
constructs.  For space reasons, we mainly provide the high-level
ideas here, and provide full formal semantics (including the soundness
proof with the extensions) in \appendixextfirst{}.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

\subsection{Type Safety}
\label{sec:extensions:types}

@@

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy |alpha|, which
maps a task list to a potentially different task list, i.e.,
$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
We described two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies based on the
current task list---in fact, our formalism can be easily
extended to consider history~\cite{BartheRRS07}.
%
As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
which always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
More precisely, our calculus generalizes to a class of deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interferent}, i.e.,
%greatest lower bound of all the labels on the task labels,\footnote{
%  The label on a task's current label is the current label of the
%  parent at the time of creation, i.e., the initial current label of
%  the task.
%}
scheduling decisions on public tasks do not depend on a sensitive task's
state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
is a task in the task list whose label is below (or incomparable to) the label
of another task, this task (or another one at the same level) must eventually
run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do not treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

More fundamentally, our scheduler parametrization is limited in being
deterministic, and thus extending the system to consider non-deterministic
schedulers (or even non-deterministic target languages) is non-trivial.
%
%For instance,  we do not consider  schedulers that, among other, rely
%on the global state |iS| or previous task configurations, as treated
%in~\cite{russo2006securing}.
%
%Additionally, our definitions rely on deterministic relations,
%
Such extensions often apply security conditions which suffer
from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
adapt non-trivial definitions as
\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
which states that a program is secure only if |l|-equivalent results are
deterministic.

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can induce external-world effects.
%
As discussed in Section~\ref{sec:real}, imposing this restriction
can be challenging.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in an IFC browser must load resources or
perform XHR to be useful.

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks, an approach taken by our Node.js
implementation.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
An alternative approach of restricting or wrapping unsafe primitives
is, for example, used in COWL and JSFlow, respectively, to allow for
controlled network communication.
%
(By restricting the default XHR object, for example, COWL allows code
to communicate with hosts according to the task's current label.)

>>>>

%while
%LIO implements a labeled file system, used in server-side web
%applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section, we show how to extend our framework with several such
constructs.  For space reasons, we mainly provide the high-level
ideas here, and provide full formal semantics (including the soundness
proof with the extensions) in \appendixextfirst{}.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

\subsection{Type Safety}
\label{sec:extensions:types}
\Red{Ale: I don't get this part. Why are we talking about type-safety? Is the
  problem that the combined semantics does not get stuck when the target does?
  Is type-safety a manner to get progress?}

@@

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy |alpha|, which
maps a task list to a potentially different task list, i.e.,
$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
We described two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies based on the
current task list---in fact, our formalism can be easily
extended to consider history~\cite{BartheRRS07}.
%
As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
which always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
More precisely, our calculus generalizes to a class of deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interferent}, i.e.,
%greatest lower bound of all the labels on the task labels,\footnote{
%  The label on a task's current label is the current label of the
%  parent at the time of creation, i.e., the initial current label of
%  the task.
%}
scheduling decisions on public tasks do not depend on a sensitive task's
state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
is a task in the task list whose label is below (or incomparable to) the label
of another task, this task (or another one at the same level) must eventually
run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do not treat more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

More fundamentally, our scheduler parametrization is limited in being
deterministic, and thus extending the system to consider non-deterministic
schedulers (or even non-deterministic target languages) is non-trivial.
%
%For instance,  we do not consider  schedulers that, among other, rely
%on the global state |iS| or previous task configurations, as treated
%in~\cite{russo2006securing}.
%
%Additionally, our definitions rely on deterministic relations,
%
Such extensions often apply security conditions which suffer
from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
adapt non-trivial definitions as
\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
where programs are secure only if |l|-equivalent results are
deterministic.

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can induce external-world effects.
%
As discussed in Section~\ref{sec:real}, imposing this restriction
can be challenging.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, COWL must load resources or perform XHR to be useful.

Like labeled references, features with external effects must be explicitly
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
%% An alternative approach is to model such effects as messages to/from
%% certain labeled tasks, an approach taken by our Node.js
%% implementation.
%% %
%% These ``special'' tasks are trusted with access to the unlabeled
%% primitives that can be used to perform the external effects; since the
%% interface to these tasks is already part of the IFC language, the
%% proof only requires showing that this task does not leak information.
%% %
Alternatively, COWL and JSFlow wrap unsafe primitives
%is, for example, used in COWL and JSFlow, respectively,
in order to allow for controlled network communication.
%
(By restricting the default XHR object, for example, COWL allows code
to communicate with hosts according to the task's current label.)
